---
title: "Info about the OSCA study programme"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = FALSE, message = FALSE)
```

```{r, code = readLines("functions.R"), cache = FALSE, include=FALSE}
```

```{r}
library(tidyverse)
library(DiagrammeR)
library(googlesheets4)
gs4_deauth()
```

## The *Operations and Supply Chain Analytics* program {#OSCA}

*Operations and Supply Chain Management* (OSCM) includes a broad area covering both manufacturing and service industries, and it involves functions such as sourcing, materials management, operations planning, distribution, logistics, retail, demand forecasting, order fulfillment, and more.


*Analytics* refers to the scientific process of transforming data into insights for making better decisions in businesses (Definition of [INFORMS.org](https://www.informs.org/About-INFORMS/News-Room/O.R.-and-Analytics-in-the-News/Best-definition-of-analytics)). 

**Operations and Supply Chain Analytics** (our program) refers to the application of the tools from analytics to handle O&SCM problems such as

* Big data management:
    * Storing, integrating, analyzing, updating, and using huge amounts of data in real time.
* Data driven decision making:
    * The process of making decisions based on actual data rather than intuition or observation alone.
* Optimization of business process:
    * Mathematical methods to find a best solution to a particular type of problem with respect to a set of desired criteria. 
* Computer simulations for business process improvement:
    * Show how systems perform under different conditions and allow users to test various ways to model a system or possible approaches to a problem.
* And many more

[link to official OSCA programme]

Måske en video ala [denne](https://www.dtu.dk/english/education/msc/programmes/business-analytics) 
eller på [denne](https://kandidat.au.dk/retailmanagement/)


```{r, include=TRUE, out.width="100%", fig.asp=NA, echo=FALSE}
g <- create_diagram(
  url = "https://docs.google.com/spreadsheets/d/1TzNty62Ae5pNiwwB2CBgnAgeFyuODGK1gxc794GPoSg/edit?usp=sharing",
  nodes = "nodes",
  edges = "edges",
  fontsize = 20)
# g %>% get_edge_df()
# g %>% get_node_df()
render_graph(g)
```





