---
title: "Info about the OSCA study programme"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = FALSE, message = FALSE)
```

```{r, code = readLines("functions.R"), cache = FALSE, include=FALSE}
```

```{r}
library(tidyverse)
library(DiagrammeR)
library(googlesheets4)
gs4_deauth()
```

## The *Operations and Supply Chain Analytics* program {#OSCA}

*Operations and Supply Chain Management* (OSCM) includes a broad area covering both manufacturing and service industries, and it involves functions such as sourcing, materials management, operations planning, distribution, logistics, retail, demand forecasting, order fulfillment, and more.


*Analytics* refers to the scientific process of transforming data into insights for making better decisions in businesses (Definition of [INFORMS.org](https://www.informs.org/About-INFORMS/News-Room/O.R.-and-Analytics-in-the-News/Best-definition-of-analytics)). 

**Operations and Supply Chain Analytics** (our program) refers to the application of the tools from analytics to handle O&SCM problems such as

* Big data management:
    * Storing, integrating, analyzing, updating, and using huge amounts of data in real time.
* Data driven decision making:
    * The process of making decisions based on actual data rather than intuition or observation alone.
* Optimization of business process:
    * Mathematical methods to find a best solution to a particular type of problem with respect to a set of desired criteria. 
* Computer simulations for business process improvement:
    * Show how systems perform under different conditions and allow users to test various ways to model a system or possible approaches to a problem.
* And many more

[link to official OSCA programme]

Måske en video ala [denne](https://www.dtu.dk/english/education/msc/programmes/business-analytics) 
eller på [denne](https://kandidat.au.dk/retailmanagement/)


```{r, include=TRUE, out.width="100%", fig.asp=NA, echo=FALSE}
g <- create_diagram(
  url = "https://docs.google.com/spreadsheets/d/1TzNty62Ae5pNiwwB2CBgnAgeFyuODGK1gxc794GPoSg/edit?usp=sharing",
  nodes = "nodes",
  edges = "edges",
  fontsize = 20)
# g %>% get_edge_df()
# g %>% get_node_df()
render_graph(g)
```


CORAL is a research cluster that seeks to contribute to further research developments in the fields of Operations Research, Business Analytics, Logistics or similar fields such as Operations Management, Management Science, Supply Chain Management, Industrial Engineering, and Decision Science at Aarhus University. Research is conducted from theoretical as well as practical perspectives.

Operations Research (OR) deals with the application of advanced analytical methods to help make better decisions. That is, OR may be seen as the application of scientific and mathematical methods to the study and analysis of problems involving complex systems. The terms management science and decision science are sometimes used as synonyms.

Business Analytics (BA) refers to the scientific process of transforming data into insights for making better decisions in companies and organizations. BA can both be seen as the complete decision making process for solving a business problem and as the creation of business value by integration of concepts, methods and data. As a process, it can be characterized by descriptive, predictive, and prescriptive model building using (big) data sources. Operations Research and Management Science are closely related to prescriptive analytics. Companies that use BA focus on fact-based management to drive their decision-making, and they treat data and information as strategic assets to be shared within the company.

Logistics and Operations Management is a cross-functional area focusing on effective and efficient flows of goods and services, and the related flows of information and cash. Supply Chain Management (SCM) adds a process-oriented and cross-company perspective. The process orientation implies emphasis on business processes like Demand Planning, Order Fulfillment, Customer Service Management and Procurement Management. The cross-company perspective focuses on the links and interfaces between the companies, e.g. vendors, manufacturers, distributors, third-party logistics providers, and the customers in a supply chain. Globalization of trade and supply chain relations adds to the challenges of, but also the potential for improved effectiveness and efficiencies of supply networks.

For further details about the specific research interests of the CORAL members, see our publications and each member’s personal webpage.

Several CORAL members teach in master's degree programmes such as Logistics and Supply Chain Management, Mathematics and Economics.


## succes stories

https://www.youtube.com/watch?v=KkVDcwzs6Ik&t=74s

https://www.informs.org/Impact/O.R.-Analytics-Success-Stories/Increasing-ride-share-efficiency-Better-outcomes-for-drivers-and-passengers

https://www.informs.org/Impact/O.R.-Analytics-Success-Stories/Improving-water-quality-with-operations-research

https://www.informs.org/Impact/O.R.-Analytics-Success-Stories/Optimizing-offshore-wind-farm-design-and-enabling-a-fossil-fuel-free-future 

https://www.informs.org/Impact/O.R.-Analytics-Success-Stories/Optimized-school-bus-routing-helps-school-districts-design-better-policies


